Deciding to Disclose

### 2015-06-19 agent_examples.tex
More trimming
Placement juggling

\section{Agent Examples}
\label{sec:agent_eg}

@@

\begin{equation*}
\begin{align*}
X &= \{10\}\\
R_{w}(l) &= \sum_{x \in X} -xp(x | l) = -10p(10 | l)\\
R_{w}(l) &= -10(\frac{\alpha_{l,10}+n_{l,10}}{\sum_{j}(\alpha_{j}+n_{j})}) = -10(\frac{1+2}{1+2})\\
R_{w}(l) &= -10(\frac{3}{3}) = -10
\end{align*}
\end{equation*}

@@

Returning to our example agent, under this model the type of the midwife becomes salient, hence \(n_{h}=3\), and \(n_{l,n}=2\), \(n_{m,n}=1\). Their prior beliefs remain uninformative, i.e. \(\alpha_{j} = 1, j \in \{l,m,h\}\), \(\alpha_{i,j}=1,i \in \{r,n\}, j \in \{l,m,h\}\). As before, the agent evaluates \(R_{w}\) for the three signals, and the process for the light signal is given below -

\begin{equation*}
\begin{align*}
R_{w}(l, l) &= \sum_{i\in A_{m}}\sum_{j\in \Theta} -u_{w}(l, i, l, j)p(j)p(i | l)\\
R_{w}(l, l) &= -u_{w}(l, r, l, l)p(l)p(r | l) - u_{w}(l, n, l, l)p(l)p(n | l) - u_{w}(l, r, l, m)p(m)p(r | l) - u_{w}(l, n, l, m)p(m)p(n | l) \\
&\phantom{{}=1}- u_{w}(l, r, l, h)p(h)p(r | l) - u_{w}(l, n, l, h)p(h)p(n | l)\\
u_{w}(l, i, l, j) &= 10\\
R_{w}(l, l) &= -10p(l)p(r | l) - 10p(l)p(n | l) - 10p(m)p(r | l) - 10p(m)p(n | l) - 10p(h)p(r | l) - 10p(h)p(n | l)\\
p(l) &= \frac{1 + 0}{1 + 1 + 1 + 3} = \frac{1}{6}\\
p(m) &= \frac{1 + 0}{1 + 1 + 1 + 3} = \frac{1}{6}\\
p(h) &= \frac{1 + 3}{1 + 1 + 1 + 3} = \frac{2}{3}\\
p(r | l) &= \frac{1 + 0}{1 + 1 + 2} = \frac{1}{4}\\
p(n | l) &= \frac{1 + 2}{1 + 1 + 2} = \frac{3}{4}\\
R_{w}(l, l) &= -10\cdot \frac{1}{6} \cdot \frac{1}{4} - 10\cdot \frac{1}{6} \cdot \frac{3}{4} - 10\cdot \frac{1}{6} \cdot \frac{1}{4} - 10\cdot \frac{1}{6} \cdot \frac{3}{4} - 10\cdot \frac{2}{3} \cdot \frac{1}{4} - 10\cdot \frac{2}{3} \cdot \frac{3}{4}\\
&= -10
\end{align*}
\end{equation*}

@@

Once again, we return to the light drinker example.  The inferential aspects are identical with the more complex Bayesian risk minimisation algorithm, hence \(p(j)p(i | l)\), and \(u_{w}(l, i, l, j)\) remain the same, but the agent additionally calculates $v(u_{w}(l, i, l, j))w^{+}(p(j))w^{+}(p(i | l))$. For the \ac{CPT} parameters, the values are those originally given by \citet{Tversky1992} and used in the actual simulations which are given fully in table \ref{tab:cpt_params}.

\begin{table}
\begin{tabular}{|l | l | c|}
\hline
Name & Description & Value \\ \hline
\(\gamma\) & Probability weighting for gains  & 0.61 \\ \hline
\(\delta\) & Probability weighting for losses &  0.69\\ \hline
\(\alpha\) & Power for gains  & 0.88 \\ \hline
\(\beta\) & Power for losses & 0.88 \\ \hline
\(\lambda\) & Loss aversion &  2.25 \\ \hline
\end{tabular}
\caption[Table caption text]{Model parameters. \label{tab:cpt_params}}
\end{table}

\begin{equation*}
\begin{align*}
\alpha &= 0.88\\
\gamma &= 0.61\\
p(l) &= \frac{1}{6}\\
p(m) &= \frac{1}{6}\\
p(h) &= \frac{2}{3}\\
p(r | l) &= \frac{1}{4}\\
p(n | l) &= \frac{3}{4}\\
u_{w}(l, i, l, j) &= 10\\
f&=(10;\frac{1}{24},10;\frac{1}{8},10;\frac{1}{24},10;\frac{1}{8},10;\frac{1}{6},10;\frac{1}{2})\\
f^{+}&=f,f^{-}=()\\
n &= 5\\
v(u_{w}) &= f(u_{w}) = u_{w}^\alpha\\
v(u_{w}) &= 10^{0.88} = 7.59\\
\pi_{0}^{+}&=w^{+}(\frac{1}{24} + \frac{1}{8} + \frac{1}{24} + \frac{1}{8} + \frac{1}{6} + \frac{1}{2}) - w^{+}(\frac{1}{8} + \frac{1}{24} + \frac{1}{8} + \frac{1}{6} + \frac{1}{2})=w^{+}(1) - w^{+}(\frac{23}{24})\\
&=0.19\\
\pi_{1}^{+}&=w^{+}(\frac{1}{8} + \frac{1}{24} + \frac{1}{8} + \frac{1}{6} + \frac{1}{2}) - w^{+}(\frac{1}{24} + \frac{1}{8} + \frac{1}{6} + \frac{1}{2})=w^{+}(\frac{23}{24}) - w^{+}(\frac{5}{6})\\
&= 0.17\\
\pi_{2}^{+}&=w^{+}(\frac{1}{24} + \frac{1}{8} + \frac{1}{6} + \frac{1}{2}) - w^{+}(\frac{1}{8} + \frac{1}{6} + \frac{1}{2})=w^{+}(\frac{5}{6}) - w^{+}(\frac{19}{24})\\
&= 0.04\\
\pi_{3}^{+}&=w^{+}(\frac{1}{8} + \frac{1}{6} + \frac{1}{2}) - w^{+}(\frac{1}{6} + \frac{1}{2})=w^{+}(\frac{19}{24}) - w^{+}(\frac{2}{3})\\
&= 0.09\\
\pi_{4}^{+}&=w^{+}(\frac{1}{6} + \frac{1}{2}) - w^{+}(\frac{1}{2})=w^{+}(\frac{2}{3}) - w^{+}(\frac{1}{2})\\
&= 0.09\\
\pi_{5}^{+}&=w^{+}(\frac{1}{2})\\
&= 0.42\\
V(f) &= V(f^{+}) + V(f^{-}) = V(f^{+}) + 0\\
V(f^{+}) &= \sum_{i}^{n}\pi_{i}^{+}(f^{+})v_{i}^{+}(f^{+}) = 7.59
\end{align*}
\end{equation*}

>>>>

%!TEX root = disclosure_game.tex
\section{Agent Examples}
\label{sec:agent_eg}

@@

\begin{equation*}
\begin{aligned}
X &= \{10\}\\
R_{w}(l) &= \sum_{x \in X} -xp(x | l) = -10p(10 | l)\\
R_{w}(l) &= -10(\frac{\alpha_{l,10}+n_{l,10}}{\sum_{j}(\alpha_{j}+n_{j})}) = -10(\frac{1+2}{1+2})\\
R_{w}(l) &= -10(\frac{3}{3}) = -10
\end{aligned}
\end{equation*}

@@

Returning to our example agent, under this model the type of the midwife becomes salient, hence \(n_{h}=3\), and \(n_{l,n}=2\), \(n_{m,n}=1\). Their prior beliefs remain uninformative, i.e. \(\alpha_{j} = 1, j \in \{l,m,h\}\), \(\alpha_{i,j}=1,i \in \{r,n\}, j \in \{l,m,h\}\). As before, the agent evaluates \(R_{w}\) for the three signals, and the process for the light signal is given below.

\begin{equation*}
\begin{aligned}
R_{w}(l, l) &= \sum_{i\in A_{m}}\sum_{j\in \Theta} -u_{w}(l, i, l, j)p(j)p(i | l)\\
R_{w}(l, l) &= -u_{w}(l, r, l, l)p(l)p(r | l) - u_{w}(l, n, l, l)p(l)p(n | l) - u_{w}(l, r, l, m)p(m)p(r | l)\\
&\phantom{{}=1}- u_{w}(l, n, l, m)p(m)p(n | l) - u_{w}(l, r, l, h)p(h)p(r | l) - u_{w}(l, n, l, h)p(h)p(n | l)\\
u_{w}(l, i, l, j) &= 10\\
R_{w}(l, l) &= -10p(l)p(r | l) - 10p(l)p(n | l) - 10p(m)p(r | l) - 10p(m)p(n | l)\\
&\phantom{{}=1} - 10p(h)p(r | l) - 10p(h)p(n | l)\\
p(l) &= \frac{1 + 0}{1 + 1 + 1 + 3} = \frac{1}{6}\\
p(m) &= \frac{1 + 0}{1 + 1 + 1 + 3} = \frac{1}{6}\\
p(h) &= \frac{1 + 3}{1 + 1 + 1 + 3} = \frac{2}{3}\\
p(r | l) &= \frac{1 + 0}{1 + 1 + 2} = \frac{1}{4}\\
p(n | l) &= \frac{1 + 2}{1 + 1 + 2} = \frac{3}{4}\\
R_{w}(l, l) &= -10\cdot \frac{1}{6} \cdot \frac{1}{4} - 10\cdot \frac{1}{6} \cdot \frac{3}{4} - 10\cdot \frac{1}{6} \cdot \frac{1}{4} - 10\cdot \frac{1}{6} \cdot \frac{3}{4} - 10\cdot \frac{2}{3} \cdot \frac{1}{4} - 10\cdot \frac{2}{3} \cdot \frac{3}{4}\\
&= -10
\end{aligned}
\end{equation*}

@@

Once again, we return to the light drinker example.  The inferential aspects are identical with the more complex Bayesian risk minimisation algorithm, hence \(p(j)p(i | l)\), and \(u_{w}(l, i, l, j)\) remain the same, but the agent additionally calculates $v(u_{w}(l, i, l, j))w^{+}(p(j))w^{+}(p(i | l))$. For the \ac{CPT} parameters, the values are those originally given by \citet{Tversky1992} and used in the actual simulations which are given in table \ref{tab:cpt_params}.

\begin{table}
\begin{tabular}{|l | l | c|}
\hline
Name & Description & Value \\ \hline
\(\gamma\) & Probability weighting for gains  & 0.61 \\ \hline
\(\delta\) & Probability weighting for losses &  0.69\\ \hline
\(\alpha\) & Power for gains  & 0.88 \\ \hline
\(\beta\) & Power for losses & 0.88 \\ \hline
\(\lambda\) & Loss aversion &  2.25 \\ \hline
\end{tabular}
\caption[Table caption text]{\ac{CPT} parameters. \label{tab:cpt_params}}
\end{table}

\begin{equation*}
\begin{aligned}
\alpha &= 0.88\\
\gamma &= 0.61\\
p(l) &= \frac{1}{6}\\
p(m) &= \frac{1}{6}\\
p(h) &= \frac{2}{3}\\
p(r | l) &= \frac{1}{4}\\
p(n | l) &= \frac{3}{4}\\
u_{w}(l, i, l, j) &= 10\\
f&=(10;\frac{1}{24},10;\frac{1}{8},10;\frac{1}{24},10;\frac{1}{8},10;\frac{1}{6},10;\frac{1}{2})\\
f^{+}&=f,f^{-}=()\\
n &= 5\\
v(u_{w}) &= f(u_{w}) = u_{w}^\alpha\\
v(u_{w}) &= 10^{0.88} = 7.59\\
\pi_{0}^{+}&=w^{+}(\frac{1}{24} + \frac{1}{8} + \frac{1}{24} + \frac{1}{8} + \frac{1}{6} + \frac{1}{2}) - w^{+}(\frac{1}{8} + \frac{1}{24} + \frac{1}{8} + \frac{1}{6} + \frac{1}{2})=w^{+}(1) - w^{+}(\frac{23}{24})\\
&=0.19\\
\pi_{1}^{+}&=w^{+}(\frac{1}{8} + \frac{1}{24} + \frac{1}{8} + \frac{1}{6} + \frac{1}{2}) - w^{+}(\frac{1}{24} + \frac{1}{8} + \frac{1}{6} + \frac{1}{2})=w^{+}(\frac{23}{24}) - w^{+}(\frac{5}{6})\\
&= 0.17\\
\pi_{2}^{+}&=w^{+}(\frac{1}{24} + \frac{1}{8} + \frac{1}{6} + \frac{1}{2}) - w^{+}(\frac{1}{8} + \frac{1}{6} + \frac{1}{2})=w^{+}(\frac{5}{6}) - w^{+}(\frac{19}{24})\\
&= 0.04\\
\pi_{3}^{+}&=w^{+}(\frac{1}{8} + \frac{1}{6} + \frac{1}{2}) - w^{+}(\frac{1}{6} + \frac{1}{2})=w^{+}(\frac{19}{24}) - w^{+}(\frac{2}{3})\\
&= 0.09\\
\pi_{4}^{+}&=w^{+}(\frac{1}{6} + \frac{1}{2}) - w^{+}(\frac{1}{2})=w^{+}(\frac{2}{3}) - w^{+}(\frac{1}{2})\\
&= 0.09\\
\pi_{5}^{+}&=w^{+}(\frac{1}{2})\\
&= 0.42\\
V(f) &= V(f^{+}) + V(f^{-}) = V(f^{+}) + 0\\
V(f^{+}) &= \sum_{i}^{n}\pi_{i}^{+}(f^{+})v_{i}^{+}(f^{+}) = 7.59
\end{aligned}
\end{equation*}

### 2015-06-19 disclosure_game.tex
Grayscale friendliness, spelling
Change info sharing to social learning
Begin moving model description to appendix. Also add an explanation of
pseudo-counts vs priors.
Simulation schedule
Reducing the pagecount
Substantially.
Trimming length
More reorganisation
Placement juggling

% RECOMMENDED %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass{svmult}

% choose options for [] as required from the list
% in the Reference Guide

\usepackage{mathptmx}       % selects Times Roman as basic font
\usepackage{helvet}         % selects Helvetica as sans-serif font
\usepackage{courier}        % selects Courier as typewriter font
\usepackage{type1cm}        % activate if the above 3 fonts are
                            % not available on your system
%
\usepackage{makeidx}         % allows index generation
\usepackage{graphicx}        % standard LaTeX graphics tool
                             % when including figure files
\usepackage{multicol}        % used for the two-column index
\usepackage[bottom]{footmisc}% places footnotes at page bottom
%\documentclass{article}
% \usepackage{tikz}
 \usepackage{adjustbox}
 \usepackage{multirow}
 \usepackage{algorithm}
 \usepackage{algpseudocode}
 \usepackage{ifthen}
 \usepackage{csquotes}
\newboolean{enable-backrefs} % enable backrefs in the bibliography
\setboolean{enable-backrefs}{true} % true false
\newcommand{\backrefnotcitedstring}{\relax}%(Not cited.)
\newcommand{\backrefcitedsinglestring}[1]{(Cited on page~#1.)}
\newcommand{\backrefcitedmultistring}[1]{(Cited on pages~#1.)}
\ifthenelse{\boolean{enable-backrefs}}%
{%
		\PassOptionsToPackage{hyperpageref}{backref}
		\usepackage{backref} % to be loaded after hyperref package
		   \renewcommand{\backreftwosep}{ and~} % separate 2 pages
		   \renewcommand{\backreflastsep}{, and~} % separate last of longer list
		   \renewcommand*{\backref}[1]{}  % disable standard
		   \renewcommand*{\backrefalt}[4]{% detailed backref
		      \ifcase #1 %
		         \backrefnotcitedstring%
		      \or%
		         \backrefcitedsinglestring{#2}%
		      \else%
		         \backrefcitedmultistring{#2}%
		      \fi}%
}{\relax}
\usepackage{comment}
 \usepackage{natbib}
 \setcitestyle{authoryear,round,aysep={,}}
% \usepackage{hyperref}
 \usepackage{graphicx}
 \usepackage[subrefformat=parens,labelformat=simple,caption=false,labelfont={bf}]{subfig}
 \usepackage[nolist,smaller]{acronym}
 \usepackage{sidecap}
% \usepackage{nomencl}

\makeindex

@@

\author{Jonathan Gray \and Jakub Bijak \and Seth Bullock}
% Use \authorrunning{Short Title} for an abbreviated version of
% your contribution title if the original one is too long
\institute{Jonathan Gray \at University of Southampton, Southampton, United Kingdom \email{j.gray@soton.ac.uk}
\and Jakub Bijak \at University of Southampton, Southampton, United Kingdom \email{j.bijak@soton.ac.uk}
\and Seth Bullock \at University of Southampton, Southampton, United Kingdom \email{sgb@ecs.soton.ac.uk}}

@@

\input{Abstract}
\acresetall

@@

\input{Background}

\input{Model}

@@

\bibliography{library,library_addendum}
\bibliographystyle{spbasic}

\appendix
\setcounter{table}{0}
\renewcommand{\thetable}{A\arabic{table}}
\input{SensitivityAnalysis}
\end{document}

>>>>

% RECOMMENDED %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass[graybox]{svmult}
\usepackage[hyperfootnotes=false]{hyperref}
\hypersetup{bookmarksdepth=3}
% choose options for [] as required from the list
% in the Reference Guide

\usepackage{mathptmx}       % selects Times Roman as basic font
\usepackage{helvet}         % selects Helvetica as sans-serif font
\usepackage{courier}        % selects Courier as typewriter font
\usepackage{type1cm}        % activate if the above 3 fonts are
                            % not available on your system
%
\usepackage{makeidx}         % allows index generation
\usepackage{graphicx}        % standard LaTeX graphics tool
                             % when including figure files
\usepackage{multicol}        % used for the two-column index
\usepackage[bottom]{footmisc}% places footnotes at page bottom
%\documentclass{article}
% \usepackage{tikz}
 \usepackage{adjustbox}
 \usepackage{multirow}
 \usepackage{algorithm}
 \usepackage{algpseudocode}
 \usepackage{ifthen}
 \usepackage{csquotes}
 \usepackage{amsmath}

\usepackage{comment}
 \usepackage{natbib}
 \setcitestyle{numbers,square}
% \usepackage{hyperref}
 \usepackage{graphicx}
 \usepackage[subrefformat=parens,labelformat=simple,caption=false,labelfont={bf}]{subfig}
 \usepackage[nolist,smaller]{acronym}
 \usepackage{sidecap}
% \usepackage{nomencl}
\makeindex

@@

\author{Jonathan Gray, Jakub Bijak, and Seth Bullock}
% Use \authorrunning{Short Title} for an abbreviated version of
% your contribution title if the original one is too long
\institute{Jonathan Gray \at University of Southampton, Southampton, United Kingdom \email{j.gray@soton.ac.uk}
\and Jakub Bijak \at University of Southampton, Southampton, United Kingdom \email{j.bijak@soton.ac.uk}
\and Seth Bullock \at University of Southampton, Southampton, United Kingdom \email{sgb@ecs.soton.ac.uk}}

@@

\input{abstract_short}
\acresetall

@@

%\input{Background}

\input{Model}
\input{agent_models}

@@

\bibliography{library,library_addendum}
\bibliographystyle{spbasic}
\input{SensitivityAnalysis}
\input{model_description}
\input{simulation_schedule}
\input{agent_examples}
\end{document}

### 2015-06-19 model_description.tex
Placement juggling

\section{Model Description}
\label{app:detail_model_description}

@@

\begin{figure}[H]
\begin{adjustbox}{center}\subfloat[Women (heavy drinkers)]{\includegraphics[width=119mm]{figures/women_influence}}\end{adjustbox}
\vskip
\begin{adjustbox}{center}\subfloat[Midwives]{\includegraphics[width=119mm]{figures/mw_influence}}\end{adjustbox}
\caption{Influence diagrams, showing the game broken into two decision problems. Squares indicate a decision node, while circles are (from the perspective of the agent) chance nodes}

>>>>

%!TEX root = disclosure_game.tex
\section{Model Description}
\label{app:model_description}

@@

\begin{figure}[H]
\centering
\subfloat[Women (heavy drinkers)]{\includegraphics[width=119mm]{figures/women_influence}}
\vskip\baselineskip
\subfloat[Midwives]{\includegraphics[width=119mm]{figures/mw_influence}}
\caption{Influence diagrams, showing the game broken into two decision problems. Squares indicate a decision node, while circles are (from the perspective of the agent) chance nodes}
